---
title: "Treehugging Study - Results"
author: "Scott Claessens"
date: "`r format(Sys.Date())`"
output: html_document
---

```{r echo=FALSE}
options(width = 100)
knitr::opts_chunk$set(echo = FALSE)
```

This document reports the results of multilevel models analysing the distribution of
"treehugging" (i.e. valuing nature more than humans) around the world.

We can plot this variable on a global map.

```{r}
tar_read(plot1)
```

# Intercept-only models

First, we fit a standard random intercept multilevel model with treehugging as
the outcome variable and random intercepts for countries and study waves.

```{r}
tar_read(m1.1)
```

We can get intra-class correlations for countries (`iso`) and study waves
(`year`). The ICC for `year` is basically 0, meaning there is no variation in
the outcome variable across study waves.

```{r}
tar_read(icc1.1a)
```

The ICC for `iso` is 0.06, meaning that 6% of the variation in treehugging is
between countries.

```{r}
tar_read(icc1.1b)
```

These ICC results mean that in future models we should retain country-level
random intercepts, but not study wave random intercepts.

In an additional random intercept model, we can fit another model to determine 
the proportion of country-level variance that can be explained by geographic and 
cultural proximity.

```{r}
tar_read(m1.2)
```

We can then calculate the proportion of country-level variance explained by
geographic and cultural proximity by calculating an ICC without including the
residual variance (`sigma`).

```{r}
tar_read(icc1.2a)
```

```{r}
tar_read(icc1.2b)
```

75% of the country-level variance can be explained by geographic proximity,
while 15% can be explained by linguistic proximity. The additional 10% is
explained by neither.

# Human Development Index (HDI)

We then fit a model that includes HDI as a standardised country-level predictor,
controlling for individual-level demographics. The outcome variable `Treehugging`
is left on the raw data scale (min = -5, max = 5).

```{r}
tar_read(m2.1)
```

There is a small positive effect of HDI. As HDI increases by one standard deviation,
the outcome variable increases by 0.08. We can visualise this effect.

```{r warning=FALSE}
tar_read(plot2)
```

Does this effect hold when controlling for geographic and cultural proximity
between countries?

```{r}
tar_read(m2.2)
```

Yes, it does.

# Environmental Performance Index (EPI)

We also fit a model that includes EPI as a standardised country-level predictor,
controlling for individual-level demographics.

```{r}
tar_read(m3.1)
```

There is a similar small positive effect of EPI. As EPI increases by one standard
deviation, the outcome variable increases by 0.11. We can visualise this effect.

```{r warning=FALSE}
tar_read(plot3)
```

Does this effect hold when controlling for geographic and cultural proximity?

```{r}
tar_read(m3.2)
```

The 95% credible interval for the slope now includes zero. But the majority of
the posterior remains positive, suggesting that the effect holds.
